---
title: "FFT EMD WT Data Window Analysis in R"
subtitle: "Report"
1 author: "Aleksandras Urbonas"
date: "2020-01-20"
review: "2020-01-21T1025"
output: html_document
---


```{r,include=F,echo=T,warning=T}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

---

# Task

1. Load data file and choose first 2^m records (65k+)
2. Iterate data window of size 2^k: 256, 512, 1024, etc.:
  + Collect statistical properties
  + Detrend data
  + Run Fast Fourier Transform on data window
  + Filter strong Fourier coefficients using threshold value
  + Perform inverse FFT
  + Trend data
  + Calculate autocorrelation for inversed FFT
3. Calculate distance between data window dw1 and all other data windows
4. Detect clusters of distances

---

## # Literature review

A literature review has been done to review the available solutions and development of scientific research in signal trasnformations.



A comparison of the Hilbert-Huang transform (HHT), the wavelet transform (WT) and the Fourier transform (FT) for analysis of the road surface profiles of three pavement profiles.
The WT and FT have been the traditional spectral analysis methods, but they are predicated on a priori selection of basis functions that are either of infinite length or have fixed finite widths.
The central idea of HHT is the EMD, which decomposes a signal into basis functions called the intrinsic mode functions (IMFs).
The Hilbert transform (HT) can then be applied to the IMFs to generate an energy–time–frequency spectrum called the Hilbert spectrum.
The strength of HHT is the ability to process non-stationary and non-linear data. Unlike the FT, which transforms information from the time domain into the frequency domain, the HHT does not lose temporal information after transformation, i.e. energy-frequency information is maintained in the time domain. This paper attempts to reveal the frequency and energy content of the road profile data with the three methods mentioned as a means to establishing the most suitable way of characterising the pavement profiles in terms of ride quality.




---


## Definition

Fast Fourier Transform (FFT) is a data processing algorithm.

---


## Assumptions

1. FFT assumes signal is periodic and it's 'basic ingredient' is various simple sine waves.
2. In FFT, our signal is changed from the time spectrum to the frequency spectrum.


---

## 1. Code:

```{r r1_1,echo=F}
x <- rnorm(100)
plot(x, type='h', main='h-plot')
```


Let us add an interactive chart with library `plotly`:

```{r r1_2,echo=F}
x <- rnorm(100)
y <- rnorm(100)
plotly::plot_ly(
  x = x
  , y = y
  , type = 'scatter'
  , mode = 'markers' #  lines
)

```


---

## 2. Text

Some text. R is a collaborative project with many contributors. Type 'contributors()' for more information and 'citation()' on how to cite R or R packages in publications.

Type 'demo()' for some demos, 'help()' for on-line help, or 'help.start()' for an HTML browser interface to help.

Type 'q()' to quit R.


---

## 3. Figures

```{r r1,echo=F}
n = 300
set.seed(123)
par(mar = c(4, 4, 0.1, 0.1))
plot(rnorm(n), rnorm(n), pch = 21, cex = 5 * runif(n), col = "white", bg = "gray")
```


---

The end.